DATA 621 - Business Analytics and Data Mining

### 2020-11-20 HW5/HW5-Draft.Rmd
Start data prep. Suggest model selection criteria

>>>>

# DATA PREPARATION
The different methods of imputation and feature generation will be discussed in
each models BUILD section. The only preparation performed here will be that
which will apply to all models equally.

# SELECT MODELS
## Model Selection Criteria
We will look at RMSE and AIC as our metrics and select the model which performs
best on both, Ties will be broken by \(R^2\).
